Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations

### 2019-09-14 notes/paper/paper.tex
revised up to section 3

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

@@

\section{Introduction}\label{sec:intro}
  Modern observational cosmology has reached a stage where constraints from most current and future datasets are limited by astrophysical systematic uncertainties, i.e. our lack of detailed understanding of the small-scale physics behind the luminous components of the Universe, galaxies and gas \citep[e.g.][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S,2014JCAP...04..028F,2015MNRAS.454.2451E,2015MNRAS.454.1958M,2015JCAP...12..049S,2019MNRAS.488.1652H,2019JCAP...03..020S,2019OJAp....2E...4C}. The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}. \MB{[why is this relevant here?]} \DA{[It's another example of where gastrophysics limits cosmology.]} Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}. Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}. Even the analysis of the temperature anisotropies in the Cosmic Microwave Background (CMB), arguably the cleanest cosmological observable, are currently limited by the impact of astrophysical foregrounds on small scales \citep{2014ApJ...782...74H,2017JCAP...06..031L,2019arXiv190712875P}.

  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address this issue \citep{2017JCAP...11..040B,2019BAAS...51c.297B}. These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure and the velocity field. Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters. This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2017PhRvD..95l3512S}. The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}. The kSZ has been used in cross-correlation with galaxy clustering to constrain the growth of structure and the gas density profile around haloes \citep{2016PhRvD..93h2002S,2016A&A...586A.140P,2016PhRvL.117e1301H,2016MNRAS.461.3172S,2017JCAP...03..008D}.

  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the Planck collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}. The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies. This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation. Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.

      Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central. This assumption breaks down in cases such as mergers, where centrals have not been established yet. Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario. We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.

      Besides their mean values, we also need to specify the statistics of $N_c$ and $N_s$. Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a binomial distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.

@@

    \subsubsection{tSZ and pressure profiles}\label{sssec:theory.hm.pe}
      In order to describe the electron pressure in a halo, we use the generalised NFW profile (GNFW) described in \cite{2010A&A...517A..92A} and used in the \planck\ tSZ cluster analysis \cite{2016A&A...594A..24P}. This profile takes the form:
      \begin{equation}
        P_e(r)=P_*\,p(r/r_{500c}),
      \end{equation}
      where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Section \ref{sssec:theory.hm.cm}). The normalisation $P_*$ is given by
      \begin{equation}\label{eq:arnaud_norm}
        P_*=6.41\,\left(1.65\,\, {\rm eV}\,{\rm cm}^{-3}\right)h_{70}^{8/3}
        \left(\frac{h_{70}(1-\bH)M_{500c}}{3\times10^{14}M_\odot}\right)^{0.79},
      \end{equation}
      where $h_{70}=H_0/(70\ {\rm km}\,{\rm s}^{-1}\,{\rm Mpc}^{-1})$, and $M_{500c}$ is the halo mass enclosed by $r_{500c}$. The GNFW form factor is
      \begin{equation}
        p(x)=(c_P x)^{-\gamma}\left[1+(c_P x)^\alpha\right]^{(\gamma-\beta)/\alpha},
      \end{equation}
      with $(\alpha,\beta,\gamma,c_P)=(1.33,4.13,0.31,1.81)$. We must note that other pressure profiles have been proposed in the literature (e.g. \citejap{2012ApJ...758...75B}), but we choose this parameterisation in order to be able to relate our measurement of $(1-\bH)$ to the results of \cite{2016A&A...594A..24P}.

      The quantity $1-\bH$ in Eq.\!~\ref{eq:arnaud_norm} parameterises our lack of knowledge about the precise relation between mass and pressure in clusters. This factor is also commonly referred to as the `hydrostatic bias', since it was originally defined to account for the fraction of halo mass not in hydrostatic equilibrium missed by X-ray observations. Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we instead refer to it as the \emph{mass bias}. Numerical simulations have constrained the mass deficit to be around 20\% (i.e. $1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is needed in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}. This will be a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.

      Within the halo model description, and assuming a log-normal $y$-mass relation, the pressure profile cumulants are given by:
      \begin{align}
        &\langle u_y(k|M)\rangle=P_e(k),\\
        &\langle u_y^2(k|M)\rangle=P_e^2(k)\,e^{\sigma_{\ln Y}^2},
      \end{align}
      where $P_e(k)$ is the Fourier transform of the GNFW profile and $\sigma_{\ln Y}=0.173\pm0.023$ is the intrinsic logarithmic scatter in the $y$-mass relation \cite{2016A&A...594A..24P}. Note that, since we do not make use of the tSZ auto-correlation, we do not use the second order cumulant of the pressure profile in our analysis. However, since we analyse the galaxy-tSZ correlation, we need to model the covariance between the galaxy overdensity and pressure profiles. For simplicity, we adopt a simple parameterisation:
      \begin{equation}
        \langle u_y(k|M) u_g(k|M)\rangle = (1+\rho_{yg})\langle u_g(k|M)\rangle \langle u_y(k|M)\rangle,
      \end{equation}
      where $\rho_{yg}$ is a free parameter that determines the sign of the correlation between galaxy abundance and pressure. Marginalising over this parameter has the added advantage of removing any sensitivity of our final constraints to $1-\bH$ on the details of the cross-spectrum model in the 1-halo regime, where both parameters are completely degenerate.

      It is also worth exploring the halo model bias (Eq.\!~\ref{eq:hm_bias}) for the Compton-$y$ parameter. At $k\rightarrow0$ it is given by:
      \begin{align}\nonumber
        \langle bP_e\rangle&=\int dM\,\frac{dn}{dM}\,b_h(M)\,\int_0^\infty dr\,4\pi r^2\,P_e(r|M)\\\label{eq:by}
               &=\int dM\,\frac{dn}{dM}\,b_h(M)\,E_T(M),
      \end{align}
      where $E_T(M)$ is the thermal energy in a halo of mass $M$ \citep{2017MNRAS.467.2315V,2019arXiv190413347P}. A measurement of $\langle bP_e\rangle$ can therefore be related to the thermodynamics of gas inside haloes \MB{[more about this relation? and, this is electron pressure - how it connects to gas pressure?]} \DA{[Eq. \ref{eq:by} is the equation linking to thermal energy. Note that electron and total pressure are just proportional to each other, I've now noted this below Eq. \ref{eq:compty}.]}. We also express our measurements in terms of this parameter in Section \ref{sec:results}.

    \subsubsection{Concentration-mass relation and mass definitions}\label{sssec:theory.hm.cm}
      Halo radii $r_\Delta$ are usually defined as the size of the sphere containing a given mass $M_\Delta$:
      \begin{equation}
        M_\Delta = \frac{4\pi}{3}\rho_*(z) \; \Delta \; r^3_\Delta.
      \end{equation}
      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$ \MB{[which one do we use?]}\DA{[We state this in the next paragraph.]}. The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.

@@

>>>>

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

@@

\section{Introduction}\label{sec:intro}
  Modern observational cosmology has reached a stage where constraints from most current and future datasets are limited by astrophysical systematic uncertainties, i.e. our lack of detailed understanding of the small-scale physics behind the luminous components of the Universe, galaxies and gas \citep[e.g.][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S,2014JCAP...04..028F,2015MNRAS.454.2451E,2015MNRAS.454.1958M,2015JCAP...12..049S,2019MNRAS.488.1652H,2019JCAP...03..020S,2019OJAp....2E...4C}. The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}. Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}. Understanding the impact of baryons in the matter power spectrum will require a better understanding of the distribution of gas in halos. Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}. Even the analysis of the temperature anisotropies in the Cosmic Microwave Background (CMB), arguably the cleanest cosmological observable, are currently limited by the impact of astrophysical foregrounds on small scales \citep{2014ApJ...782...74H,2017JCAP...06..031L,2019arXiv190712875P}.

  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}. These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure and the velocity field. Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters. This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}. The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}. The kSZ has been used in cross-correlation with galaxy clustering to constrain the growth of structure and the gas density profile around haloes \citep{2016PhRvD..93h2002S,2016A&A...586A.140P,2016PhRvL.117e1301H,2016MNRAS.461.3172S,2017JCAP...03..008D}.

  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the \planck\ collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}. The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies. This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation. Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$. Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central. This assumption breaks down in cases such as mergers, where centrals have not been established yet. We will however explore departures from this fiducial model.

      Besides their mean values, we also need to specify the statistics of $N_c$ and $N_s$. Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a Bernoulli distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.

@@

    \subsubsection{tSZ and pressure profiles}\label{sssec:theory.hm.pe}
      In order to describe the electron pressure in a halo, we use the generalised NFW profile (GNFW) described in \cite{2010A&A...517A..92A} and used in the \planck\ tSZ cluster analysis \citep{2016A&A...594A..24P}. This profile takes the form:
      \begin{equation}
        P_e(r)=P_*\,p(r/r_{500c}),
      \end{equation}
      where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Section \ref{sssec:theory.hm.cm}). The normalisation $P_*$ is given by
      \begin{equation}\label{eq:arnaud_norm}
        P_*=6.41\,\left(1.65\,\, {\rm eV}\,{\rm cm}^{-3}\right)h_{70}^{8/3}
        \left(\frac{h_{70}(1-\bH)M_{500c}}{3\times10^{14}M_\odot}\right)^{0.79},
      \end{equation}
      where $h_{70}=H_0/(70\ {\rm km}\,{\rm s}^{-1}\,{\rm Mpc}^{-1})$, and $M_{500c}$ is the halo mass enclosed by $r_{500c}$. The GNFW form factor is
      \begin{equation}
        p(x)=(c_P x)^{-\gamma}\left[1+(c_P x)^\alpha\right]^{(\gamma-\beta)/\alpha},
      \end{equation}
      with $(\alpha,\beta,\gamma,c_P)=(1.33,4.13,0.31,1.81)$. We must note that other pressure profiles have been proposed in the literature (e.g. \citejap{2012ApJ...758...75B}), but we choose this parameterisation in order to be able to relate our measurement of $(1-\bH)$ to the results of \cite{2016A&A...594A..24P}.

      The quantity $1-\bH$ in Eq.\!~\ref{eq:arnaud_norm} parameterises our lack of knowledge about the precise relation between mass and pressure in clusters. This factor is also commonly referred to as the `hydrostatic bias', since it was originally defined to account for the fraction of halo mass not in hydrostatic equilibrium missed by X-ray observations. Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we instead refer to it as the {\sl mass bias}. Numerical simulations have constrained the mass deficit to be around 20\% (i.e. $1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is needed in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}. This will be a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.

      Within the halo model description, and assuming a log-normal $y$-mass relation, the pressure profile cumulants are given by:
      \begin{align}
        &\langle u_y(k|M)\rangle=P_e(k),\\
        &\langle u_y^2(k|M)\rangle=P_e^2(k)\,e^{\sigma_{\ln Y}^2},
      \end{align}
      where $P_e(k)$ is the Fourier transform of the GNFW profile and $\sigma_{\ln Y}=0.173\pm0.023$ is the intrinsic logarithmic scatter in the $y$-mass relation \cite{2016A&A...594A..24P}. Note that, since we do not make use of the tSZ auto-correlation, we do not use the second order cumulant of the pressure profile in our analysis. However, since we analyse the galaxy-tSZ correlation, we need to model the covariance between the galaxy overdensity and pressure profiles. For simplicity, we adopt a one-parameter model:
      \begin{equation}
        \langle u_y(k|M) u_g(k|M)\rangle = (1+\rho_{yg})\langle u_g(k|M)\rangle \langle u_y(k|M)\rangle,
      \end{equation}
      where the free parameter $\rho_{yg}$ determines the sign of the correlation between galaxy abundance and pressure. Marginalising over this parameter has the added advantage of removing any sensitivity of our final constraints to $1-\bH$ on the details of the cross-spectrum model in the 1-halo regime, where both parameters are completely degenerate.

      It is also worth exploring the halo model bias (Eq.\!~\ref{eq:hm_bias}) for the Compton-$y$ parameter. At $k\rightarrow0$ it is given by:
      \begin{align}\nonumber
        \langle bP_e\rangle&=\int dM\,\frac{dn}{dM}\,b_h(M)\,\int_0^\infty dr\,4\pi r^2\,P_e(r|M)\\\label{eq:by}
               &=\int dM\,\frac{dn}{dM}\,b_h(M)\,E_T(M),
      \end{align}
      where $E_T(M)$ is the thermal energy in a halo of mass $M$ \citep{2017MNRAS.467.2315V,2019arXiv190413347P}. A measurement of $\langle bP_e\rangle$ can therefore be related to the thermodynamics of gas inside haloes. We also express our measurements in terms of this parameter in Section \ref{sec:results}.

    \subsubsection{Concentration-mass relation and mass definitions}\label{sssec:theory.hm.cm}
      Halo radii $r_\Delta$ are usually defined as the size of the sphere containing a given mass $M_\Delta$:
      \begin{equation}
        M_\Delta = \frac{4\pi}{3}\rho_*(z) \; \Delta \; r^3_\Delta.
      \end{equation}
      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$. The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.

@@

  \todo{ Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario. We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.}
